Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Update plotting details

\subsection{Plotting Details}
We saved snapshots in intervals of $0.005$ in the time units of the
simulation, $\textrm{kpc}/(\textrm{km}/\textrm{s})$, which is very nearly
equal to $1\,\textrm{Gyr}$ (it is $\sim0.977\,\textrm{Gyr}$). Therefore,
throughout this work we referred to the native code time unit as
$\textrm{Gyr}$. None of our results are sensitive to this choice.

We applied a Savitzky-Golay filter \citep{1964AnaCh..36.1627S} as implemented in
\texttt{scipy} using a window length of $21$ and polynomial order of $3$ to the
plot of torques (Fig.~\ref{fig:prop}) and angle differences
(Fig.~\ref{fig:wake}) in order to remove some numerical noise.

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/torque_ps.pdf}
    \caption{Average torque exerted by gas on a bar which rotates at a fixed
    pattern speed. Since only gas within the corotation radius is able to infall
    and slower bars have larger corotation radii, slower bars experience a
    larger net torque than faster bars. The setup of the simulations used here
    is identical to the \SMUGGLE{} case discussed earlier, except the \Nbody{} disk
    is rotated as a solid body with a constant angular
    velocity.}
    \label{fig:equil}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/ps_star.pdf}
    \caption{{\bf Pattern speed evolution of a model in which we instaneously
    add stars instead of gas to the simulation, with the same density profile as
    the gas phase. The pattern speed evolution in this case is qualitatively
    similar to that of the $N$-body case, with a slight offset in the pattern
    speed. This test demonstrates that the stable pattern speed evolution in the
    SMUGGLE case is not simply a consequence of the change in potential imposed
    in our initial conditions.}}
\label{fig:ps-star}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=9cm]{fig/surf_dens.pdf}
    \caption{The time evolution of the atomic gas surface density
    (\textit{upper}), molecular gas surface density (\textit{middle}) and the
    star formation rate (SFR) surface density (\textit{lower}) at various times
    during our fiducial simulation. Colored lines indicate the profiles at
    selected times during the simulation while the black dashed lines indicate
    observations for the atomic gas \citep{2008AA...487..951K} and black dotted
    lines indicate a model which allows the CO-to-H$_2$ conversion factor
    $X_{\textrm{CO}}$ to vary with metallicity \citep{2022ApJ...929L..18E}.
    Molecular gas surface densities were provided separately (N. Evans, private
    communication). We see that the molecular gas and SFR surface densities are
    within an order of magnitude of the Milky Way's typical values at all times.
    We see a sharp decrease in the gas and SFR surface densities along the
    extent of the bar from $\sim1$ to $\sim4\,\textrm{kpc}$, related to the gas
    inflow in this region.}
    \label{fig:surf}
\end{figure}

>>>>

\subsection{Plotting Details}
We saved snapshots in intervals of $0.005$ in the time units of the simulation,
$\textrm{kpc}/(\textrm{km}/\textrm{s})$, which is very nearly equal to
$1\,\textrm{Gyr}$ (it is $\sim0.977\,\textrm{Gyr}$). Therefore, throughout this
work we referred to the native code time unit as $\textrm{Gyr}$. None of our
results are sensitive to this choice. We applied a Savitzky-Golay filter
\citep{1964AnaCh..36.1627S} as implemented in \texttt{scipy} using a window
length of $21$ and polynomial order of $3$ to the plot of torques
(Fig.~\ref{fig:prop} and Fig.~\ref{fig:sam-torque}) and angle differences
(Fig.~\ref{fig:wake}) in order to remove some numerical noise.

@@

\begin{figure*}
    \centering
    \includegraphics[width=9cm]{fig/torque_ps.pdf}
    \caption{Average torque exerted by gas on a bar which rotates at a fixed
    pattern speed. Since only gas within the corotation radius is able to infall
    and slower bars have larger corotation radii, slower bars experience a
    larger net torque than faster bars. The setup of the simulations used here
    is identical to the \SMUGGLE{} case discussed earlier, except the \Nbody{} disk
    is rotated as a solid body with a constant angular
    velocity.}
    \label{fig:equil}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=9cm]{fig/ps_star.pdf}
    \caption{{\bf Pattern speed evolution of a model in which we instaneously
    add stars instead of gas to the simulation, with the same density profile as
    the gas phase. The pattern speed evolution in this case is qualitatively
    similar to that of the $N$-body case, with a slight offset in the pattern
    speed. This test demonstrates that the stable pattern speed evolution in the
    SMUGGLE case is not simply a consequence of the change in potential imposed
    in our initial conditions.}}
\label{fig:ps-star}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=9cm]{fig/surf_dens.pdf}
    \caption{The time evolution of the atomic gas surface density
    (\textit{upper}), molecular gas surface density (\textit{middle}) and the
    star formation rate (SFR) surface density (\textit{lower}) at various times
    during our fiducial simulation. Colored lines indicate the profiles at
    selected times during the simulation while the black dashed lines indicate
    observations for the atomic gas \citep{2008AA...487..951K} and black dotted
    lines indicate a model which allows the CO-to-H$_2$ conversion factor
    $X_{\textrm{CO}}$ to vary with metallicity \citep{2022ApJ...929L..18E}.
    Molecular gas surface densities were provided separately (N. Evans, private
    communication). We see that the molecular gas and SFR surface densities are
    within an order of magnitude of the Milky Way's typical values at all times.
    We see a sharp decrease in the gas and SFR surface densities along the
    extent of the bar from $\sim1$ to $\sim4\,\textrm{kpc}$, related to the gas
    inflow in this region.}
    \label{fig:surf}
\end{figure*}
